`mathml`: Translate R Expressions to MathML and LaTeX

### 2023-06-20 rj/mathml.Rmd
The Sections of the Vignette have been reorganized.

The currently supported R\ objects are listed below, roughly following the order
proposed by [@murrell2000].

@@

This package allows R\ to render its terms in pretty mathematical equations. It
extends the current features of R\ and existing packages for displaying
mathematical formulas in R\ [@murrell2000;@allaire2018]), but most
importantly, \pkg{mathml} bridges the gap between computational needs,
presentation of results, and their reproducibility. The package supports both
MathML and LaTeX/MathJax for use in R\ Markdown documents, presentations and
Shiny App webpages.

@@

`math/2` operates like macro that translates one mathematical
element (here, `pbinom(K, N, Pi)`) to another mathematical element,
namely `fn(Name, (Args ; Pars))`. The low-level predicate `ml/3` is used to
convert these basic elements to MathML.

>>>>

The currently supported R\ objects are listed below, roughly following the order
proposed by Murrell and Ihaka [-@murrell2000].

@@

This package allows R\ to render its terms in pretty mathematical equations. It
extends the current features of R\ and existing packages for displaying
mathematical formulas in R\ [@murrell2000], but most
importantly, \pkg{mathml} bridges the gap between computational needs,
presentation of results, and their reproducibility. The package supports both
MathML and LaTeX/MathJax for use in R\ Markdown documents, presentations and
Shiny App webpages.

@@

`math/2` operates like a macro that translates one mathematical
element (here, `pbinom(K, N, Pi)`) to another mathematical element,
namely `fn(Name, (Args ; Pars))`. The low-level predicate `ml/3` is used to
convert these basic elements to MathML.
